A Systematic Literature Review on Extensions to the Role-Based Access Control Reference Model

### 2014-04-22 paper/review/breakdown.tex
My comments on review comments (breakdown) Addressed some of comments.

\item Broken literature references in Table 5

\item Tables 3,4,5 are not sorted in any order

\item Additional figures/visualizations would help

\item Reference section has incomplete entries

\item Spelling, grammar and punctuation flaws

\item Table 6 should be revised to have better structure

@@

\item This section should be shortened to at most 1 page.

\item Definitions of static and dynamic separation of duty are incorrect.

@@

  \begin{itemize}
    \item ACM Transactions on Information and System Security (TISSEC)
    \item International Conference on Emerging Security Information, Systems and Technologies, SECURWARE
    \item International Conference on Information Systems Security
    \item International Conference on Network and System Security
    \item ACM Symposium on Access Control Models and Technologies (SACMAT)
    \item ACM Symposium on Information, Computer and Communications Security
    \item Information Security Conference
    \item International Conference on Information Security and Assurance
    \item International Conference on Information Systems Security
    \item International Conference on Information Assurance and Security
  \end{itemize}

@@

\item Not clear how the authors established the common terms.

@@

\item Was this done ad hoc (during paper reading) or as a preparatory step?

\item Authors defined the classification criteria by observation during paper reading.

@@

@@

\item How do the answers to this RQ relate to the SLR?

\item This section reads like a discussion based on authors intuitions or conjectures

@@

\item Why do the authors only distinguish between enterprise/prototype implementations?

@@

\item What about other evaluation techniques such as case studies, static and dynamic analysis, formal proofs or controller experiments for example?

@@

\item Authors suggestion of "propositional logic" is purely discussion and not backed by any data from the SLR

@@

\item Why the "Hu \& Scarfone" metrics?

\item Did the authors perform a prior comparative analysis of different metrics?

>>>>

\item Broken literature references in Table 5
We address this issue.

\item Tables 3,4,5 are not sorted in any order
We manually sort by the order of the paper.

\item Additional figures/visualizations would help
[TBD] Eric and I would discuss this issue because the reviewer did not clearly which kinds of figures/visualizations would be needed.

\item Reference section has incomplete entries
We address this comment by looking at the each reference item and find missing entry. We check each entry with ACM or IEEE Bibtex. Consistent formatting will be done as well.

\item Spelling, grammar and punctuation flaws
We address this by spell check and grammar check (in Latex compiler). In addition, we convert it to MS word for additional spell check and grammar check. After this step, we will conduct manual proof reading.

\item Table 6 should be revised to have better structure
[TBD]  Eric and I would discuss this issue because the reviewer did not clearly mention what's the issue or how to revise Table 6.

@@

\item This section should be shortened to at most 1 page.
We address this comment by revising the background section.

\item Definitions of static and dynamic separation of duty are incorrect.
We find reference of static and dynamic separation of duty from NIST RBAC standard. We refer to "The NIST Model for Role-Based Access Control: Towards A Unified Standard."

@@

  \begin{itemize}
    \item ACM Transactions on Information and System Security (TISSEC)
    \item International Conference on Emerging Security Information, Systems and Technologies, SECURWARE
    \item International Conference on Information Systems Security
    \item International Conference on Network and System Security
    \item ACM Symposium on Access Control Models and Technologies (SACMAT)
    \item ACM Symposium on Information, Computer and Communications Security
    \item Information Security Conference
    \item International Conference on Information Security and Assurance
    \item International Conference on Information Systems Security
    \item International Conference on Information Assurance and Security
    \item International Symposium on Policies for Distributed Systems and Networks
    \item ACM Conference on Data and Application Security and Privacy
  \end{itemize}

@@

\item Not clear how the authors established the common terms.
We find the terms by bottom-up approach by looking at the paper and finding common terms that can characterize the paper.

@@

\item Was this done ad hoc (during paper reading) or as a preparatory step?
We address this issue by describing our approach. We do it by bottom-up search to find terms and construct it. Need to find such a method for classification (I don't think that our approach is ad-hoc if we find it during paper reading).

\item Authors defined the classification criteria by observation during paper reading.
Same as above.

@@

In our SLR, we measure not only access control policies, but also measure approaches of papers.
There are some such as "Hu \& Scarfone" metrics to measure access control policies themselves. We may find some papers that describe metrics. However, their metrics are limited to measure a specific property (such as complexity) of a given access control policy.

@@

\item How do the answers to this RQ relate to the SLR?
We address this issue by checking SLR process to understand what kinds of answers would be expected. Then, we adjust our answers to fit to SLR.

\item This section reads like a discussion based on authors intuitions or conjectures
We would move this section to discussion section if this one may not fit well to the RQs for SLR.

@@

\item Why do the authors only distinguish between enterprise/prototype implementations?
In the development process, modeling -> research prototype -> implementations in the real world systems.
Our selected papers dealt with modeling of access control policies. Then, we would like to check whether this model is provided with a prototype and implementation.

@@

\item What about other evaluation techniques such as case studies, static and dynamic analysis, formal proofs or controller experiments for example?
We find from bottom-up approach.

@@

\item Authors suggestion of "propositional logic" is purely discussion and not backed by any data from the SLR
We find reference paper about this propositional logic, which is used for papers collected for us.

@@

\item Why the "Hu \& Scarfone" metrics?
We use this metric to show additional metrics.

\item Did the authors perform a prior comparative analysis of different metrics?
[TBD]

### 2014-04-22 paper/sections/analysis.tex
My comments on review comments (breakdown) Addressed some of comments.

\textbf{Implementation Type} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Enterprise
&
\cite{motta03:contextual}
\cite{aich09:role}
\cite{yao2008task}
&
3 \\ \cline{1-3}
Prototype
& 
\cite{cholewka00:acontext-sensitive}
\cite{huang06:pervasive}
\cite{bao08:role}
\cite{zhou2007team}
&
4 \\ \cline{1-3}
None
&
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{yamazaki04:designing}
\cite{jian2008extended}
\cite{thein2011leveraging}
\cite{zou2009crbac}
\cite{haibo05:context}
\cite{zhang06:collaborative}
\cite{ni2010privacy}
\cite{masoumzadeh2008purbac}
\cite{damiani2007geo}
\cite{ray2006lrbac}
\cite{hansen2003spatial}
\cite{aich07:STARBAC}
\cite{chen08:spatio-temporal}
\cite{samuel07:spatio-temporal}
\cite{chandran05:llt}
\cite{ray07:spatio}
\cite{oh2003task}
\cite{joshi05:generalized}
&
20 \\

@@

\textbf{Evaluation Type} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Time-Based Performance
&
\cite{ni2010privacy}
\cite{aich09:role}
&
2 \\ \cline{1-3}
Complexity Analysis
&
\cite{bao08:role}
\cite{zhang06:collaborative}
\cite{chen08:spatio-temporal}
\cite{aich07:STARBAC}
&
4 \\ \cline{1-3}
Comparison to Standard RBAC
& 
\cite{bao08:role}
\cite{zou2009crbac}
\cite{zhang06:collaborative}
\cite{zhao2008flexible}
\cite{ray07:spatio}
&
5 \\ \cline{1-3}
Mathematical Modeling
& 
\cite{damiani2007geo}
\cite{hansen2003spatial}
\cite{aich07:STARBAC}
\cite{chen08:spatio-temporal}
\cite{joshi05:generalized}
&
5 \\ \cline{1-3}
Example Scenarios of the Model in Action
& 
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{cholewka00:acontext-sensitive}
\cite{huang06:pervasive}
\cite{bao08:role}
\cite{jian2008extended}
\cite{yamazaki04:designing}
\cite{zou2009crbac}
\cite{ray07:spatio}
\cite{samuel07:spatio-temporal}
\cite{joshi05:generalized}
\cite{yao2008task}
\cite{zhou2007team}
\cite{oh2003task}
&
14 \\ \cline{1-3}
Case Study of the Model in Practice
&
\cite{motta03:contextual}
&
1 \\ \cline{1-3}
None
&
\cite{masoumzadeh2008purbac}
\cite{chandran05:llt}
\cite{ray2006lrbac}
&
3 \\ \cline{1-3}

@@

\textbf{Domain} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Medical Domain
&
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{motta03:contextual}
\cite{ni2010privacy}
\cite{damiani2007geo}
\cite{hansen2003spatial}
\cite{samuel07:spatio-temporal}
\cite{aich09:role}
\cite{zhou2007team}
&
9 \\ \cline{1-3}
Pervasive Computing Environments
& 
\cite{huang06:pervasive}
\cite{chen08:spatio-temporal}
\cite{ray07:spatio}
&
3 \\ \cline{1-3}
Web Applications
& 
\cite{masoumzadeh2008purbac}
\cite{haibo05:context}
&
1 \\ \cline{1-3}
Mobile Computing
& 
\cite{thein2011leveraging}
\cite{zou2009crbac}
\cite{chandran05:llt}
\cite{aich09:role}
\cite{ray2006lrbac}
&
4 \\ \cline{1-3}
Organizations with Many Sub-departments
& 
\cite{yamazaki04:designing}
\cite{yao2008task}
&
2 \\ \cline{1-3}
Enterprise Workflows
&
\cite{cholewka00:acontext-sensitive}
\cite{bao08:role}
\cite{zhang06:collaborative}
\cite{oh2003task}
\cite{joshi05:generalized}
&
5 \\ \cline{1-3}
None
&
\cite{jian2008extended}
\cite{aich2007:STARBAC}
&
2 \\ \cline{1-3}

>>>>

\textbf{Implementation Type} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Enterprise
&
\cite{motta03:contextual}
\cite{aich09:role}
\cite{yao2008task}
&
3 \\ \cline{1-3}
Prototype
& 
\cite{cholewka00:acontext-sensitive}
\cite{huang06:pervasive}
\cite{bao08:role}
\cite{zhou2007team}
&
4 \\ \cline{1-3}
None
&
\cite{ni2010privacy}
\cite{jian2008extended}
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{yamazaki04:designing}
\cite{thein2011leveraging}
\cite{zou2009crbac}
\cite{haibo05:context}
\cite{zhang06:collaborative}
\cite{masoumzadeh2008purbac}
\cite{damiani2007geo}
\cite{ray2006lrbac}
\cite{hansen2003spatial}
\cite{aich07:STARBAC}
\cite{chen08:spatio-temporal}
\cite{samuel07:spatio-temporal}
\cite{chandran05:llt}
\cite{ray07:spatio}
\cite{oh2003task}
\cite{joshi05:generalized}
&
20 \\

@@

\textbf{Evaluation Type} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Time-Based Performance
&
\cite{ni2010privacy}
\cite{aich09:role}
&
2 \\ \cline{1-3}
Complexity Analysis
&
\cite{bao08:role}
\cite{zhang06:collaborative}
\cite{aich07:STARBAC}
\cite{chen08:spatio-temporal}
&
4 \\ \cline{1-3}
Comparison to Standard RBAC
& 
\cite{bao08:role}
\cite{zou2009crbac}
\cite{zhang06:collaborative}
\cite{ray07:spatio}
\cite{zhao2008flexible}
&
5 \\ \cline{1-3}
Mathematical Modeling
& 
\cite{damiani2007geo}
\cite{hansen2003spatial}
\cite{aich07:STARBAC}
\cite{chen08:spatio-temporal}
\cite{joshi05:generalized}
&
5 \\ \cline{1-3}
Example Scenarios of the Model in Action
&
\cite{jian2008extended}
\cite{yao2008task}
\cite{cholewka00:acontext-sensitive}
\cite{huang06:pervasive}
\cite{bao08:role}
\cite{zhou2007team} 
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{yamazaki04:designing}
\cite{zou2009crbac}
\cite{samuel07:spatio-temporal}
\cite{ray07:spatio}
\cite{joshi05:generalized}
\cite{oh2003task}
&
14 \\ \cline{1-3}
Case Study of the Model in Practice
&
\cite{motta03:contextual}
&
1 \\ \cline{1-3}
None
&
\cite{masoumzadeh2008purbac}
\cite{ray2006lrbac}
\cite{chandran05:llt}
&
3 \\ \cline{1-3}

@@

\textbf{Domain} & \textbf{Papers} & \textbf{Count} \\ \cline{1-3}
Medical Domain
&
\cite{ni2010privacy}
\cite{motta03:contextual}
\cite{aich09:role}
\cite{zhou2007team}
\cite{alam06:constraint}
\cite{tzelepi01:flexible}
\cite{damiani2007geo}
\cite{hansen2003spatial}
\cite{samuel07:spatio-temporal}

&
9 \\ \cline{1-3}
Pervasive Computing Environments
& 
\cite{huang06:pervasive}
\cite{ray07:spatio}
\cite{chen08:spatio-temporal}
&
3 \\ \cline{1-3}
Web Applications
&
\cite{haibo05:context} 
\cite{masoumzadeh2008purbac}
&
1 \\ \cline{1-3}
Mobile Computing
&
\cite{aich09:role} 
\cite{thein2011leveraging}
\cite{zou2009crbac}
\cite{ray2006lrbac}
\cite{chandran05:llt}
&
4 \\ \cline{1-3}
Organizations with Many Sub-departments
&
\cite{yao2008task} 
\cite{yamazaki04:designing}
&
2 \\ \cline{1-3}
Enterprise Workflows
&
\cite{cholewka00:acontext-sensitive}
\cite{bao08:role}
\cite{zhang06:collaborative}
\cite{oh2003task}
\cite{joshi05:generalized}
&
5 \\ \cline{1-3}
None
&
\cite{jian2008extended}
\cite{aich07:STARBAC}
&
2 \\ \cline{1-3}
